---
title: "Home Work 1: about Data Science"
format: html
editor: visual
---

# What do you think being a data scientist is about?

I think being a data scientist to it's core,  is all about extracting insights and solving problems using data.

A data scientist is involved in the tasks below (this is not an exhaustive list )

- Cleaning data
- Transforming data
- Visualizing 
- Building models
- Communicating findings 

# What differences/similarities do you see between data scientists and statisticians?

Data scientists and statisticians both deal with cleaning, transforming, modeling, visualizing, interpreting and communicating the data.However, the type of data the two deal with (structured vs unstructured, big data) and the tools that they use can be different. 

# How do you view yourself in relation to these two areas?

At my work, I'm used to dealing  with a more structured, well designed and smaller data ,doing descriptive and inferential statistics. But I also like to challenge my self and learn more data science tools. 

#Probabilty desnsity function:
```{r}
y <- density(iris$Petal.Width)

```

# Determine the class, type, and structure of the object y
```{r}
class(y)
typeof(y)
str(y)
```

#Plot y

```{r}
#| echo: false
plot(y)
```

The `echo: false` option disables the printing of code (only output is displayed).

